Estimating the socio-environmental impacts of car substitution by bicycle and public transit using open tools

### 2023-09-21 paper/PaperTRA_ETRR/PaperTRA.tex
move to full paper TRA

\documentclass[sn-basic,pdflatex]{sn-jnl}

@@

%% Per the spinger doc, new theorem styles can be included using built in style, 
%% but it seems the don't work so commented below
%\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}%
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

%% \theoremstyle{thmstyletwo}%
\theoremstyle{remark}
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

%% \theoremstyle{thmstylethree}%
\theoremstyle{definition}
\newtheorem{definition}{Definition}%

@@

\title[Article Title runing]{Article Title}

@@

\author*[1,2]{\pfx{Dr.} \fnm{Leading} \spfx{van} \sur{Author} \sfx{III} \tanm{Poet
Laureate} \dgr{MSc,
PhD}}\email{\href{mailto:abc@def}{\nolinkurl{abc@def}}}

\author[2]{\fnm{Second} \sur{Author} }

  \affil*[1]{\orgdiv{Department}, \orgname{Organization}, \orgaddress{\city{City}, \country{Country}, \postcode{100190}, \state{State}, \street{Street}}}
  \affil*[2]{\orgname{Other Organisation}}

\abstract{\textbf{Purpose}: The abstract serves both as a general
introduction to the topic and as a brief, non-technical summary of the
main results and their implications. The abstract must not include
subheadings (unless expressly permitted in the journal's Instructions to
Authors), equations or citations. As a guide the abstract should not
exceed 200 words. Most journals do not set a hard limit however authors
are advised to check the author instructions for the journal they are
submitting to.

\textbf{Methods:} The abstract serves both as a general introduction to
the topic and as a brief, non-technical summary of the main results and
their implications. The abstract must not include subheadings (unless
expressly permitted in the journal's Instructions to Authors), equations
or citations. As a guide the abstract should not exceed 200 words. Most
journals do not set a hard limit however authors are advised to check
the author instructions for the journal they are submitting to.

\textbf{Results:} The abstract serves both as a general introduction to
the topic and as a brief, non-technical summary of the main results and
their implications. The abstract must not include subheadings (unless
expressly permitted in the journal's Instructions to Authors), equations
or citations. As a guide the abstract should not exceed 200 words. Most
journals do not set a hard limit however authors are advised to check
the author instructions for the journal they are submitting to.

\textbf{Conclusion:} The abstract serves both as a general introduction
to the topic and as a brief, non-technical summary of the main results
and their implications. The abstract must not include subheadings
(unless expressly permitted in the journal's Instructions to Authors),
equations or citations. As a guide the abstract should not exceed 200
words. Most journals do not set a hard limit however authors are advised
to check the author instructions for the journal they are submitting
to.\}}

\keywords{key, dictionary, word}

\pacs[JEL Classification]{D8, H51}
\pacs[MSC Classification]{35A01, 65L10}

@@

The Introduction section, of referenced text \citet{bib1} expands on the
background of the work (some overlap with the Abstract is acceptable).
The introduction should not include subheadings.

Springer Nature does not impose a strict layout as standard however
authors are advised to check the individual requirements for the journal
they are planning to submit to as there may be journal-level
preferences. When preparing your text please also be aware that some
stylistic choices are not supported in full text XML (publication
version), including coloured font. These will not be replicated in the
typeset article if it is accepted.

\hypertarget{sec2}{%
\section{Results}\label{sec2}}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\hypertarget{sec3}{%
\section{This is an example for first level head---section
head}\label{sec3}}

\hypertarget{subsec2}{%
\subsection{This is an example for second level head---subsection
head}\label{subsec2}}

\hypertarget{subsubsec2}{%
\subsubsection{This is an example for third level head---subsubsection
head}\label{subsubsec2}}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text.

\hypertarget{sec4}{%
\section{Equations}\label{sec4}}

Equations in \LaTeX~can either be inline or on-a-line by itself
(``display equations''). For inline equations use the \texttt{\$...\$}
commands. E.g.: The equation \(H\psi = E \psi\) is written via the
command \texttt{\$H\ \textbackslash{}psi\ =\ E\ \textbackslash{}psi\$}.

For display equations (with auto generated equation numbers) one can use
the equation or align environments:

\begin{equation}
\|\tilde{X}(k)\|^2 \leq\frac{\sum\limits_{i=1}^{p}\left\|\tilde{Y}_i(k)\right\|^2+\sum\limits_{j=1}^{q}\left\|\tilde{Z}_j(k)\right\|^2 }{p+q}.\label{eq1}
\end{equation}

where, \begin{align}
D_\mu &=  \partial_\mu - ig \frac{\lambda^a}{2} A^a_\mu \nonumber \\
F^a_{\mu\nu} &= \partial_\mu A^a_\nu - \partial_\nu A^a_\mu + g f^{abc} A^b_\mu A^a_\nu \label{eq2}
\end{align}

Notice the use of \texttt{\textbackslash{}nonumber} in the align
environment at the end of each line, except the last, so as not to
produce equation numbers on lines where no equation numbers are
required. The \texttt{\textbackslash{}label\{\}} command should only be
used at the last line of an align environment where
\texttt{\textbackslash{}nonumber} is not used.

\begin{equation}
Y_\infty = \left( \frac{m}{\textrm{GeV}} \right)^{-3}
    \left[ 1 + \frac{3 \ln(m/\textrm{GeV})}{15}
    + \frac{\ln(c_2/5)}{15} \right]
\end{equation}

The class file also supports the use of
\texttt{\textbackslash{}mathbb\{\}},
\texttt{\textbackslash{}mathscr\{\}} and
\texttt{\textbackslash{}mathcal\{\}} commands. As such
\texttt{\textbackslash{}mathbb\{R\}},
\texttt{\textbackslash{}mathscr\{R\}} and
\texttt{\textbackslash{}mathcal\{R\}} produces \(\mathbb{R}\),
\(\mathscr{R}\) and \(\mathcal{R}\) respectively (refer
Subsubsection~\ref{subsubsec2}).

\hypertarget{sec5}{%
\section{Tables}\label{sec5}}

Tables can be inserted via the normal \texttt{knitr::kable()} function
or other table-generating packages.

\begin{table}

\caption{\label{tab:tab1}Caption text}
\centering
\begin{tabular}[t]{r|r}
\hline
temperature & pressure\\
\hline
0 & 0.0002\\
\hline
20 & 0.0012\\
\hline
40 & 0.0060\\
\hline
60 & 0.0300\\
\hline
80 & 0.0900\\
\hline
100 & 0.2700\\
\hline
\end{tabular}
\end{table}

Tables can also be inserted via the normal table and tabular
environment. To put footnotes inside tables you should use
\texttt{\textbackslash{}footnotetext{[}{]}\{...\}} tag. The footnote
appears just below the table itself (refer
Tables\textasciitilde{}\ref{tab1} and \ref{tab2}). For the corresponding
footnotemark use \texttt{\textbackslash{}footnotemark{[}...{]}}

\begin{table}[h]
\caption{Caption text}\label{tab1}%
\begin{tabular}{@{}llll@{}}
\toprule
Column 1 & Column 2  & Column 3 & Column 4\\
\midrule
row 1    & data 1   & data 2  & data 3  \\
row 2    & data 4   & data 5\footnotemark[1]  & data 6  \\
row 3    & data 7   & data 8  & data 9\footnotemark[2]  \\
\botrule
\end{tabular}
\footnotetext{Source: This is an example of table footnote. This is an example of table footnote.}
\footnotetext[1]{Example for a first table footnote. This is an example of table footnote.}
\footnotetext[2]{Example for a second table footnote. This is an example of table footnote.}
\end{table}

\noindent The input format for the above table is as follows:

\begin{verbatim}
\begin{table}[<placement-specifier>]
\caption{<table-caption>}\label{<table-label>}%
\begin{tabular}{@{}llll@{}}
\toprule
Column 1 & Column 2 & Column 3 & Column 4\\
\midrule
row 1 & data 1 & data 2  & data 3 \\
row 2 & data 4 & data 5\footnotemark[1] & data 6 \\
row 3 & data 7 & data 8  & data 9\footnotemark[2]\\
\botrule
\end{tabular}
\footnotetext{Source: This is an example of table footnote.
This is an example of table footnote.}
\footnotetext[1]{Example for a first table footnote.
This is an example of table footnote.}
\footnotetext[2]{Example for a second table footnote.
This is an example of table footnote.}
\end{table}
\end{verbatim}

\begin{table}[h]
\caption{Example of a lengthy table which is set to full textwidth}\label{tab2}
\begin{tabular*}{\textwidth}{@{\extracolsep\fill}lcccccc}
\toprule%
& \multicolumn{3}{@{}c@{}}{Element 1\footnotemark[1]} & \multicolumn{3}{@{}c@{}}{Element 2\footnotemark[2]} \\\cmidrule{2-4}\cmidrule{5-7}%
Project & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ \\
\midrule
Element 3  & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$\\
Element 4  & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$\\
\botrule
\end{tabular*}
\footnotetext{Note: This is an example of table footnote. This is an example of table footnote this is an example of table footnote this is an example of~table footnote this is an example of table footnote.}
\footnotetext[1]{Example for a first table footnote.}
\footnotetext[2]{Example for a second table footnote.}
\end{table}

\vfill\eject

In case of double column layout, tables which do not fit in single
column width should be set to full text width. For this, you need to use
\texttt{\textbackslash{}begin\{table*\}} \texttt{...}
\texttt{\textbackslash{}end\{table*\}} instead of
\texttt{\textbackslash{}begin\{table\}} \texttt{...}
\texttt{\textbackslash{}end\{table\}} environment. Lengthy tables which
do not fit in textwidth should be set as rotated table. For this, you
need to use \texttt{\textbackslash{}begin\{sidewaystable\}} \texttt{...}
\texttt{\textbackslash{}end\{sidewaystable\}} instead of
\texttt{\textbackslash{}begin\{table*\}} \texttt{...}
\texttt{\textbackslash{}end\{table*\}} environment. This environment
puts tables rotated to single column width. For tables rotated to double
column width, use \texttt{\textbackslash{}begin\{sidewaystable*\}}
\texttt{...} \texttt{\textbackslash{}end\{sidewaystable*\}}.

\begin{sidewaystable}
\caption{Tables which are too long to fit, should be written using the "sidewaystable" environment as shown here}\label{tab3}
\begin{tabular*}{\textheight}{@{\extracolsep\fill}lcccccc}
\toprule%
& \multicolumn{3}{@{}c@{}}{Element 1\footnotemark[1]}& \multicolumn{3}{@{}c@{}}{Element\footnotemark[2]} \\\cmidrule{2-4}\cmidrule{5-7}%
Projectile & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ & Energy & $\sigma_{calc}$ & $\sigma_{expt}$ \\
\midrule
Element 3 & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$ \\
Element 4 & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$ \\
Element 5 & 990 A & 1168 & $1547\pm12$ & 780 A & 1166 & $1239\pm100$ \\
Element 6 & 500 A & 961  & $922\pm10$  & 900 A & 1268 & $1092\pm40$ \\
\botrule
\end{tabular*}
\footnotetext{Note: This is an example of table footnote this is an example of table footnote this is an example of table footnote this is an example of~table footnote this is an example of table footnote.}
\footnotetext[1]{This is an example of table footnote.}
\end{sidewaystable}

\hypertarget{sec6}{%
\section{Figures}\label{sec6}}

As per the \LaTeX~standards you need to use eps images for
\LaTeX~compilation and \texttt{pdf/jpg/png} images for \texttt{PDFLaTeX}
compilation. Use the \texttt{dev} knitr option to use the approrpate
format. This is one of the major difference between \LaTeX~and
\texttt{PDFLaTeX}. Each image should be from a single input .eps/vector
image file. Avoid using subfigures. The command for inserting images for
\LaTeX~and \texttt{PDFLaTeX} can be generalized. The package used to
insert images in \texttt{LaTeX/PDFLaTeX} is the graphicx package.
Figures can be inserted via the normal figure environment as shown in
the below example:

\begin{figure}
\includegraphics{skeleton_files/figure-latex/fig1-1} \caption{This is an example of a caption}\label{fig:fig1}
\end{figure}

\hypertarget{sec7}{%
\section{Algorithms, Program codes and Listings}\label{sec7}}

Packages \texttt{algorithm}, \texttt{algorithmicx} and
\texttt{algpseudocode} are used for setting algorithms in \LaTeX~using
the format:

\begin{verbatim}
\begin{algorithm}
\caption{<alg-caption>}\label{<alg-label>}
\begin{algorithmic}[1]
. . .
\end{algorithmic}
\end{algorithm}
\end{verbatim}

You may refer above listed package documentations for more details
before setting \texttt{algorithm} environment. For program codes, the
``program'' package is required and the command to be used is
\texttt{\textbackslash{}begin\{program\}} \texttt{...}
\texttt{\textbackslash{}end\{program\}}. A fast exponentiation
procedure:

Similarly, for \texttt{listings}, use the \texttt{listings} package.
\texttt{\textbackslash{}begin\{lstlisting\}} \texttt{...}
\texttt{\textbackslash{}end\{lstlisting\}} is used to set environments
similar to \texttt{verbatim} environment. Refer to the
\texttt{lstlisting} package documentation for more details.

A fast exponentiation procedure:

\lstset{texcl=true,basicstyle=\small\sf,commentstyle=\small\rm,mathescape=true,escapeinside={(*}{*)}}
\begin{lstlisting}
begin
  for $i:=1$ to $10$ step $1$ do
      expt($2,i$);  
      newline() od                (*\textrm{Comments will be set flush to the right margin}*)
where
proc expt($x,n$) $\equiv$
  $z:=1$;
  do if $n=0$ then exit fi;
     do if odd($n$) then exit fi;                 
        comment: (*\textrm{This is a comment statement;}*)
        $n:=n/2$; $x:=x*x$ od;
     { $n>0$ };
     $n:=n-1$; $z:=z*x$ od;
  print($z$). 
end
\end{lstlisting}

\begin{algorithm}
\caption{Calculate $y = x^n$}\label{algo1}
\begin{algorithmic}[1]
\Require $n \geq 0 \vee x \neq 0$
\Ensure $y = x^n$ 
\State $y \Leftarrow 1$
\If{$n < 0$}\label{algln2}
        \State $X \Leftarrow 1 / x$
        \State $N \Leftarrow -n$
\Else
        \State $X \Leftarrow x$
        \State $N \Leftarrow n$
\EndIf
\While{$N \neq 0$}
        \If{$N$ is even}
            \State $X \Leftarrow X \times X$
            \State $N \Leftarrow N / 2$
        \Else[$N$ is odd]
            \State $y \Leftarrow y \times X$
            \State $N \Leftarrow N - 1$
        \EndIf
\EndWhile
\end{algorithmic}
\end{algorithm}

\begin{minipage}{\hsize}

\lstset{frame=single,framexleftmargin=-1pt,framexrightmargin=-17pt,framesep=12pt,linewidth=0.98\textwidth,language=pascal}

\begin{lstlisting}
for i:=maxint to 0 do begin \{ do nothing \} end; Write(`Case
insensitive'); Write(`Pascal keywords.');

\end{lstlisting}

\end{minipage}

\hypertarget{sec8}{%
\section{Cross referencing}\label{sec8}}

Figures and tables are labeled with a prefix (fig or tab, respectively)
plus the chunk label. Other environments such as equation and align can
be labelled via the \texttt{\textbackslash{}label\{\#label\}} command
inside or just below the \texttt{\textbackslash{}caption\{\}} command.
You can then use the label for cross-reference. As an example, consider
the chunk label declared for Figure~\ref{fig:fig1} which is fig1. To
cross-reference it, use the command
\texttt{Figure\ \textbackslash{}ref\{fig:fig1\}}, for which it comes up
as ``Figure~\ref{fig:fig1}''.

To reference line numbers in an algorithm, consider the label declared
for the line number 2 of Algorithm~\ref{algo1} is
\texttt{\textbackslash{}label\{algln2\}}. To cross-reference it, use the
command \texttt{\textbackslash{}ref\{algln2\}} for which it comes up as
line~\ref{algln2} of Algorithm~\ref{algo1}.

\hypertarget{subsec7}{%
\subsection{Details on reference citations}\label{subsec7}}

For citations of references, use~\citet{bib1} or \citep{bib2}.

\hypertarget{sec10}{%
\section{Examples for theorem like environments}\label{sec10}}

The documentclass for springer \texttt{sn-jnl.cls} contains 3 styling
that you can use to set new default for theorems and proofs type

\begin{description}
\item[\texttt{thmstyleone}]
Numbered, theorem head in bold font and theorem text in italic style
\item[\texttt{thmstyletwo}]
Numbered, theorem head in roman font and theorem text in italic style
\item[\texttt{thmstylethree}]
Numbered, theorem head in bold font and theorem text in roman style
\end{description}

For mathematics journals, theorem styles can be included as shown in the
following examples.

\begin{theorem}
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text.

\end{theorem}

To add labels and subheadings, use LaTeX notation

\begin{theorem}[Theorem subhead]\label{thm1}
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text. Example theorem text.
Example theorem text. Example theorem text.

\end{theorem}

Other environments are proposition, example, remark, definition, proof
and quote

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\begin{proposition}
Example proposition text. Example proposition text. Example proposition
text. Example proposition text. Example proposition text. Example
proposition text. Example proposition text. Example proposition text.
Example proposition text. Example proposition text.

\end{proposition}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\begin{example}
Phasellus adipiscing semper elit. Proin fermentum massa ac quam. Sed
diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas
lacinia. Nam ipsum ligula, eleifend at, accumsan nec, suscipit a, ipsum.
Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem.

\end{example}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\begin{remark}
Phasellus adipiscing semper elit. Proin fermentum massa ac quam. Sed
diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas
lacinia. Nam ipsum ligula, eleifend at, accumsan nec, suscipit a, ipsum.
Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem.

\end{remark}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\begin{definition}[Definition sub head]
Example definition text. Example definition text. Example definition
text. Example definition text. Example definition text. Example
definition text. Example definition text. Example definition text.

\end{definition}

Additionally a predefined ``proof'' environment is available. This
prints a ``Proof'' head in italic font style and the ``body text'' in
roman font style with an open square at the end of each proof
environment.

\begin{proof}
Example for proof text. Example for proof text. Example for proof text.
Example for proof text. Example for proof text. Example for proof text.
Example for proof text. Example for proof text. Example for proof text.
Example for proof text.

\end{proof}

Sample body text. Sample body text. Sample body text. Sample body text.
Sample body text. Sample body text. Sample body text. Sample body text.

\hypertarget{sec11}{%
\section{Methods}\label{sec11}}

@@

\hypertarget{sec12}{%
\section{Discussion}\label{sec12}}

Discussions should be brief and focused. In some disciplines use of
Discussion or `Conclusion' is interchangeable. It is not mandatory to
use both. Some journals prefer a section `Results and Discussion'
followed by a section `Conclusion'. Please refer to Journal-level
guidance for any specific requirements.

@@

@@

@@

\bmhead{Supplementary information}

If your article has accompanying supplementary file/s please state so
here.

Authors reporting data from electrophoretic gels and blots should supply
the full unprocessed scans for key as part of their Supplementary
information. This may be requested by the editorial team/s if it is
missing.

@@

\begin{flushleft}
Editorial Policies for:

\noindent Springer journals and proceedings:
\url{https://www.springer.com/gp/editorial-policies}

\noindent Nature Portfolio journals:
\url{https://www.nature.com/nature-research/editorial-policies}

\noindent \textit{Scientific Reports}:
\url{https://www.nature.com/srep/journal-policies/editorial-policies}

\noindent BMC journals:
\url{https://www.biomedcentral.com/getpublished/editorial-policies}

\end{flushleft}

\begin{appendices}

\hypertarget{secA1}{%
\section{Section title of first appendix}\label{secA1}}

An appendix contains supplementary information that is not an essential
part of the text itself but which may be helpful in providing a more
comprehensive understanding of the research problem or it is information
that is too cumbersome to be included in the body of the paper.

For submissions to Nature Portfolio Journals please use the heading
``Extended Data''.

\end{appendices}

>>>>

\documentclass[sn-apa,referee,pdflatex]{sn-jnl}

@@

@@

\title[]{Estimating the socio-environmental impacts of car substitution
by bicycle and public transit using open tools}

@@

\author*[1]{\fnm{Rosa} \sur{Félix} }\email{\href{mailto:rosamfelix@tecnico.ulisboa.pt}{\nolinkurl{rosamfelix@tecnico.ulisboa.pt}}}

\author[1]{\fnm{Filipe} \sur{Moura} }\email{\href{mailto:fmoura@tecnico.ulisboa.pt}{\nolinkurl{fmoura@tecnico.ulisboa.pt}}}

\author[2]{\fnm{Robin} \sur{Lovelace} }\email{\href{mailto:r.lovelace@leeds.ac.uk}{\nolinkurl{r.lovelace@leeds.ac.uk}}}

  \affil*[1]{\orgdiv{CERIS - Instituto Superior
Técnico}, \orgname{University of
Lisbon}, \orgaddress{\city{Lisbon}, \country{Portugal}, \postcode{1049-001}, \street{Av
Rovisco Pais 1}}}
  \affil[2]{\orgdiv{Institute for Transport
Studies}, \orgname{University of
Leeds}, \orgaddress{\city{Leeds}, \country{United
Kingdom}, \postcode{LS2 9JT}, \street{34-40 University Rd}}}

\abstract{In metropolitan areas, car trips can be replaced by a
combination of public transit and cycling for the first-and-last mile.
This approach requires interventions to make cycling more appealing, and
the resulting public investments can have significant social and
environmental benefits. This paper focuses on estimating the potential
for cycling + PT as a substitute for car trips in the Lisbon
metropolitan area and assessing its socio-environmental impacts using
open data and open source tools.

To achieve the cycling targets set by the Portuguese cycling strategy,
the Department of Transport introduced \emph{biclaR}, a decision support
tool that facilitates the design and development of a metropolitan
cycling network. A scenario of intermodality introduced, and its
socio-environmental impacts were assessed using the \emph{HEAT for
Cycling} and the \emph{HEAT as a Service} tools. Additionally, we
estimated the impacts of shifting car trips to PT and monetize them with
the EU Guide to cost-benefit analysis.

The results indicate that 20\% of the current trips can be made with the
bicycle + PT combination, with an additional 12\% of PT trips being
potentially replaced. Shifting to cycling for the first-and-last mile
can reduce annual CO2eq emissions by 6,000 to 15,000 tons/day, and the
10-year socio-environmental benefits account for €230 to €590 million,
depending on the cycling targets. For the PT leg, the transfer from car
results in the avoidance of 8,500 to 20,800 tons of CO2eq emissions per
year.

The provided information on socio-economic benefits can support
policymakers in prioritizing interventions to reduce the reliance on
individual motorized transportation and effectively communicate their
decisions.}

\keywords{Active transport, Intermodality, First and last mile, Health
economic assessment, Environmental impacts, Open data and methods}

@@

The Introduction section should explain the background to the study, its
aims, a summary of the existing literature and why this study was
necessary.

In metropolitan areas, car trips can be replaced by a combination of
public transit (PT) and cycling for the first-and-last mile. This
approach requires interventions and programs to make bicycling more
appealing, and the resulting public investments can have significant
social and environmental benefits. This paper focuses on estimating the
potential for cycling + PT as a substitute for car trips in the Lisbon
metropolitan area (LMA) and assessing its socio-environmental impacts
using open data and open source tools.

According to the latest mobility survey conducted in 2018, the LMA
registered a total of 5.3 million daily trips, with only 0.5\% by
bicycle. Car modal share is 58.4\%, while PT accounts for 15.5\%. To
achieve the cycling targets set by the Portuguese national cycling
strategy for 2025 and 2030 (4\% and 10\%, respectively), the Department
of Transport introduced biclaR, a decision support tool that facilitates
the design and development of a metropolitan cycling network.

The intermodality scenario considers trips that can combine PT and
cycling for the first-and-last legs. Conservatively, we considered the
sum of first-and-last legs up to 5 km. Furthermore, we restricted PT use
to unimodal trips without transfers (although they can be included in
future modeling). Finally, we only included PT modes that can
practically accommodate bicycles, such as trains, ferries, trams, and
intermunicipal bus lines with bike racks (Figure 1).

To obtain reliable results, we used the OpenStreetMap road network and
GTFS data. The r5r R package estimated the trip duration and distance
for both the original modes and the bicycle + PT combination, while the
od jittering R package estimated the OD locations based on a
centroid-based OD matrix.

Socio-environmental impacts were assessed using the HEAT for Cycling and
the HEAT as a Service tools, from the WHO. Additionally, we estimate the
impacts of shifting car trips to PT for the second leg of the journey
with EMEP/EEA's COPERT methodology and monetize them with the EU Guide
to cost-benefit analysis.

The results indicate that 20\% of the current trips can be made with the
bicycle + PT combination, with an additional 12\% of PT trips being
potentially replaced. Shifting to cycling for the first-and-last mile
can reduce annual CO2eq emissions by 6,000 to 15,000 tons/day, and the
10-year socio-environmental benefits account for €230 to €590 million,
depending on the cycling targets. For the PT leg, the transfer from car
results in the avoidance of 8,500 to 20,800 tons of CO2eq emissions per
year, or €1.4 to €3.5 million over 10 years, with trains offering the
greatest potential for substitution (88\%).

By making the research process publicly accessible in a code repository,
this study enables the replication of similar estimates for
socio-environmental impacts resulting from a modal shift from cars to
bicycles + PT in other metropolitan areas. The provided information on
socio-economic benefits can support policymakers in prioritizing
interventions to reduce the reliance on individual motorized
transportation and effectively communicate their decisions.

\hypertarget{sec2}{%
\section{Methods}\label{sec2}}

The methods section should include:

\begin{itemize}
\tightlist
\item
  the aim, design and setting of the study
\item
  the characteristics of participants or description of materials
\item
  a clear description of all processes and methodologies employed.
  Generic names should generally be used. When proprietary * brands are
  used in research, include the brand names in parentheses
\item
  the type of statistical analysis used, including a power calculation
  if appropriate
\item
  studies involving human participants, data or tissue or animals must
  include statement on ethics approval and consent
\end{itemize}

\hypertarget{sec11}{%
\section{Results and Discussion}\label{sec11}}

@@

@@

This should state clearly the main conclusions and provide an
explanation of the importance and relevance of the study to the field.

@@

This is a test \citet{felix2023} to check if they show up.

@@

@@
